---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 2"
author: "Mahb 2"
date: "10/19/2022"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1 - Denny's in AK

```{r}

dn_ak <- dennys %>% filter(state == "AK")
nrow(dn_ak)

```

### Exercise 2 - La Quinta in AK

```{r}

lq_ak <- laquinta %>% filter(state == "AK") 
nrow(lq_ak)

```

### Exercise 3 - Join Denny's and La Quinta in AK

```{r}

dn_lq_ak <- full_join(dn_ak, lq_ak, by = "state") 

```

...

### Exercise 4 - Read AK Dataframe

```{r}
dn_lq_ak
```

There are 6 observations with 11 variables.
The 11 variables are address (x & y), city(x & y), zip(x & y), longitude(x & y), latitude(x & y), and state.
The x in the variable name is the data from the 'x' data frame which is associated with the Denny's, and 'y' is associated with La Quinta

...

### Exercise - Import the Haversine function

```{r}
haversine <- function(long1, lat1, long2, lat2, round = 3) {
  # convert to radians
  long1 = long1 * pi / 180
  lat1  = lat1  * pi / 180
  long2 = long2 * pi / 180
  lat2  = lat2  * pi / 180
  R = 6371 # Earth mean radius in km
  a = sin((lat2 - lat1)/2)^2 + cos(lat1) * cos(lat2) * sin((long2 - long1)/2)^2
  d = R * 2 * asin(sqrt(a))
  return( round(d,round) ) # distance in km
}

```

...

### Exercise 6 - Calculate the Distances

```{r}

dn_lq_ak <- dn_lq_ak %>% mutate(distance_km = haversine(longitude.x, latitude.x, longitude.y, latitude.y))

```

...

### Exercise 7

```{r}
dn_lq_ak_mindist <- dn_lq_ak %>%
  group_by(address.x) %>%
  summarise(closest = min(distance_km))
```

...

### Exercise 8

```{r}
dn_lq_ak %>% ggplot(aes(x=address.x, y=distance_km)) + geom_point()
```

```{r}
dn_lq_ak_mindist %>% ggplot(aes(x=address.x, y=closest)) + geom_point()
```

...

### Exercise 9

```{r}
dn_nc <- dennys %>% filter(state == "NC")
lq_nc <- laquinta %>% filter(state == "NC") 
dn_lq_nc <- full_join(dn_nc, lq_nc, by = "state") 
dn_lq_nc <- dn_lq_nc %>% mutate(distance_km = haversine(longitude.x, latitude.x, longitude.y, latitude.y))
dn_lq_nc_mindist <- dn_lq_nc %>%
  group_by(address.x) %>%
  summarise(closest = min(distance_km))
dn_lq_nc %>% ggplot(aes(x=address.x, y=distance_km)) + geom_point()
dn_lq_nc_mindist %>% ggplot(aes(x=address.x, y=closest)) + geom_point()
```

...

### Exercise 10

```{r}
dn_tx <- dennys %>% filter(state == "TX")
lq_tx <- laquinta %>% filter(state == "TX") 
dn_lq_tx <- full_join(dn_tx, lq_tx, by = "state") 
dn_lq_tx <- dn_lq_tx %>% mutate(distance_km = haversine(longitude.x, latitude.x, longitude.y, latitude.y))
dn_lq_tx_mindist <- dn_lq_tx %>%
  group_by(address.x) %>%
  summarise(closest = min(distance_km))
dn_lq_tx %>% ggplot(aes(x=address.x, y=distance_km)) + geom_point()
dn_lq_tx_mindist %>% ggplot(aes(x=address.x, y=closest)) + geom_point()
```

...

### Exercise 11

```{r}
dn_ca <- dennys %>% filter(state == "CA")
lq_ca <- laquinta %>% filter(state == "CA") 
dn_lq_ca <- full_join(dn_ca, lq_ca, by = "state") 
dn_lq_ca <- dn_lq_ca %>% mutate(distance_km = haversine(longitude.x, latitude.x, longitude.y, latitude.y))
dn_lq_ca_mindist <- dn_lq_ca %>%
  group_by(address.x) %>%
  summarise(closest = min(distance_km))
dn_lq_ca %>% ggplot(aes(x=address.x, y=distance_km)) + geom_point()
dn_lq_ca_mindist %>% ggplot(aes(x=address.x, y=closest)) + geom_point()
dn_lq_ca_mindist %>% filter(closest <= 1)
```

...

### Exercise 12

Kind of ...
