---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Liam Durkin"
date: "17 October 2022"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

Load in the Denny's and La Quinta Data

```{r}
df_dennys <- dennys
df_laquinta <- laquinta
```

Reading the rows and columns of Denny's

```{r}
nrow(df_dennys)
ncol(df_dennys)
```

Each row in the Denny's dataset represents a Denny's location.
The variables are address, city, state, zip, longitute, and latitude.

### Exercise 2

Reading the rows and columns of La Quinta

```{r}
nrow(df_laquinta)
ncol(df_laquinta)
```

Each row in the Denny's dataset represents a La Quinta location.
The variables are address, city, state, zip, longitute, and latitude.

### Exercise 3

There are La Quinta's outside of the US in the countries of Mexico, Canada, and Honduras

There are Denny's outside of the US in the countries of Mexico, Canada, Puerto Rico, and Indonesia.

...

### Exercise 4

If the State is not one of the 50 US states then we would know that it is not in the US.

The longitude and latitude location could be check to see if its within the boundaries of the US.

The zip code location could be checked.

...

### Exercise 5

```{r}
denny_non_us <- df_dennys %>% filter(!(state %in% states$abbreviation))
```

The Denny's listed in this data set do not have a location outside of the US.

...

### Exercise 6

```{r}
df_dennys <- df_dennys %>% mutate(country = "United States")
```

...

### Exercise 7

```{r}
laquinta_non_us <- df_laquinta %>% filter(!(state %in% states$abbreviation))
```

There are 14 laquinta locations outside of the US.
They are in Mexico, Colombia, and Canada.
...

### Exercise 8

```{r}
df_laquinta <- df_laquinta %>% 
  mutate(country = case_when(
    state %in% state.abb ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT" ~ "Colombia",
    state %in% c("AG", "QR", "CH", "NL", "VE", "PU", "SL", "FM") ~ "Mexico"
))
```

...

### Exercise 9

```{r}
dennys_num <- df_dennys %>% count(state) %>% inner_join(states, by = c("state" = "abbreviation"))
```

California has the most Denny's locations, and Delaware has the least amount of Denny's locations.

```{r}
laquinta_num <- df_laquinta %>% count(state) %>% inner_join(states, by = c("state" = "abbreviation"))
```

Texas has the most amount of La Quinta's, and Maine has the least amount of La Quinta's.

...

### Exercise 10

```{r}
df_dennys <- df_dennys %>%
  mutate(establishment = "Denny's")
df_laquinta <- df_laquinta %>%
  mutate(establishment = "La Quinta")

dn_lq <- bind_rows(df_dennys, df_laquinta)

dn_lq %>% ggplot(mapping = aes(x = longitude, y = latitude, color = establishment)) + geom_point()
```

...

### Exercise 11

```{r}
df_dennys <- df_dennys %>%
  mutate(establishment = "Denny's")
df_laquinta <- df_laquinta %>%
  mutate(establishment = "La Quinta")

dn_lq <- bind_rows(df_dennys, df_laquinta) %>%
<<<<<<< HEAD
  filter(state == "OK")
=======
  filter(state == "NC")
>>>>>>> c22f7093988991c809b608d62f8275752cde21b0

dn_lq %>% ggplot(mapping = aes(x = longitude, y = latitude, color = establishment)) + geom_point()
```

...

### Exercise 12

```{r}
df_dennys <- df_dennys %>%
  mutate(establishment = "Denny's")
df_laquinta <- df_laquinta %>%
  mutate(establishment = "La Quinta")

dn_lq <- bind_rows(df_dennys, df_laquinta) %>%
  filter(state == "TX")

dn_lq %>% ggplot(mapping = aes(x = longitude, y = latitude, color = establishment)) + geom_point()
```

...

Add exercise headings as needed.
