---
title: "Airline_Durkin"
author: "Liam Durkin"
date: "`r Sys.Date()`"
output: html_document
---

Class play with NYC flights data.

## Load Packages

```{r}
library(nycflights13)
library(tidyverse)
library(here)
library(janitor)
library(dplyr)
```

## Load flight data
Load the Flight Data Into R
```{r}
thisfile=here("data_raw","DL_SelectFields_2017.zip")
df2017=read_csv(thisfile) %>% clean_names()

thisfile=here("data_raw","airline_data_2018.zip")
df2018=read_csv(thisfile) %>% clean_names()

thisfile=here("data_raw","DL_SelectFields_2019.zip")
df2019=read_csv(thisfile) %>% clean_names()

thisfile=here("data_raw","DL_SelectFields_2020.zip")
df2020=read_csv(thisfile) %>% clean_names()

thisfile=here("data_raw","airline_data_2021_updated.zip")
df2021=read_csv(thisfile) %>% clean_names()

thisfile=here("data_raw","DL_SelectFields2022.zip")
df2022=read_csv(thisfile) %>% clean_names()


```

Join The Data
```{r}
delta_data = df2017 %>% bind_rows(df2018) %>% bind_rows(df2019) %>% bind_rows(df2020) %>% bind_rows(df2021) %>% bind_rows(df2022)

```


Mutate Some of the Data to Get Desired Results
```{r}

delta_data_2 <- mutate(delta_data, month_since = month + 12*(year-2017)) %>% filter(airline_id == "19790")

df_sum = delta_data_2 %>% group_by(month_since) %>% 
    summarise(total_pass = sum(passengers), num_flights = sum(departures_performed)) %>% 
    mutate(avg_pass_per_flight = total_pass/num_flights )


```


```{r}
df_sum %>% ggplot(aes(month_since)) + geom_bar(aes(weight = avg_pass_per_flight)) + ggtitle("Delta Airlines Average Passengers Per Flight By Month Since 2017")

```
This data shows the average passengers per flight per month since 2017 based on Delta Airlines.  From this information, we should be able to speculate future numbers, patterns, and historical information based on what we have here.  It seems as though Delta is not back into full swing from the covid pandemic, or they are growing larger than usual.  The next coming months will tell us more.








